Title Goes Here

### 2022-01-25 analysis/paper/paper.Rmd
test

@@

>>>>

# Abstract

Flaked stone artefacts from Southeast Asia typically lack visually distinctive and strongly
patterned forms, which can make them challenging to analyze and interpret. As a result,
many of the cultural dynamics of Pleistocene hunter-gatherers of this region are poorly
understood. We use 2D shape data to hypothesize a relationship between unretouched
flake shape and assemblage reduction intensity at Mau A, an early Holocene archaeo-
logical site in northern Vietnam. We apply a Principal Components Analysis to the flake
outlines to investigate shape variation throughout the reduction sequence (measured
by dorsal cortex coverage). We find that flake shape varies by reduction stage, primarily
through differences in flake length and width. Our results suggest that flake shape is
sensitive to assemblage reduction intensity, and may give useful comparative insights
when other attributes show little variation. These results are important for understanding
stone artefact assemblages from Southeast Asia which often yield little variation when
analysed with traditional approaches.

@@

- Flake shape is often related to the uses of said flakes (insert citations here)
- Stone tools from South East Asia tend to lack the distinctive outlines of European tools (insert citations here)
- Flake outline analysis was condu
